---
title: 'Early Vote Election 2020: Poll Place Service Dashboard'
runtime: shiny
output:
  html_document:
    df_print: paged
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
    social: menu
    source_code: https://github.com/francine-stephens/election2020
    theme: simplex
---

```{r setup, include=FALSE}

library(shiny)
library(tidyverse)
library(leaflet) # devtools::install_github('rstudio/leaflet')
library(plotly) # devtools::install_github('ropensci/plotly')
library(ggplot2) # devtools::install_github('hadley/ggplot2')
library(dplyr)
library(flexdashboard) # devtools::install_github('rstudio/flexdashboard')
library(rgeos)
library(maptools)
library(readr)
library(ggthemes)
library(viridis)

### Read in data for tab 1, and subset for the selected county
poll_locs <- readRDS("ev_locs_top2tiers.rds")
precincts_voter_data <- readRDS("precinct_voter_data_top_counties.rds")


# Generate data for the second tab
isochrones <- readRDS("ev_10_min_drive_iso_info.rds")


```

Sidebar {.sidebar}
======================================================================

Use the __Polling Places & Precincts__ tab to explore the distribution of early vote polling locations and voter characteristics of precincts for your chosen county.  The red line on the scatterplot represents a locally-weighted estimate of how diversity varies in the metropolitan area by distance from its urban core or cores.  Click and drag on the scatterplot to highlight the corresponding precincts on the map below.

Click the __Polling Place Service Areas__ tab to examine the characteristics of the citizen-voting age population that is served by a 10 minute drive from the polling location. To learn more about the project, click the __About__ tab.  

Application author: [Francine Stephens](https://sociology.stanford.edu/people/francine-stephens).


Bell
======================================================================

Row 
-----------------------------------------------------------------------

### Map of Likely Democrat Voters

```{r}
# Draw the map without selected tracts
dem_pal <- colorNumeric(
  palette = "Blues",
  domain = precincts_voter_data$pct_likely_dem
)

leaflet() %>%
    addMapboxTiles(
      style_id = "streets-v11",
      username = "mapbox"
    ) %>%
    addPolygons(
      data = precincts_voter_data %>%
      st_transform(., crs = wgs),
      color = ~dem_pal(pct_likely_dem),
      label = ~county_name
    ) %>% 
    addCircles(
      data = tx_early_vote_2tiers_sf %>% st_transform(., crs = wgs),
      color = "red",
      label = ~location_name 
    ) %>%
     addPolygons(
      data = tx_counties_top2_tiers_sf %>% select(CNTY_NM == "Bell") %>%
      st_transform(., crs = wgs),
      color = "black", 
      weight = 1, 
      fill = FALSE,
      label = ~CNTY_NM
    )

```


```{r}

# Draw the poc map without selected tracts
output$poc_map <- renderLeaflet({
  
    pal <- colorNumeric(viridis(999), NULL)
    
    map_poc <- leaflet(county_precincts()) %>%
      addProviderTiles('CartoDB.Positron') %>%
      clearShapes() %>%
      addPolygons(stroke = FALSE, smoothFactor = 0, 
                  fillColor = ~pal(pct_poc), fillOpacity = 0.7, 
                  layerId = ~dnc_id) %>% 
      addMarkers(data = county_polls,
                 popup = ~as.character(location_name), label = ~as.character(location_name))
      addLegend(position = 'bottomright', pal = pal, 
                values = county_precincts()$pct_poc, title = '% Likely Democrat')
    
    map_poc
    
  })

# Click event for the map (will use to generate chart)
click_precinct <- eventReactive(input$map_shape_click, {

    x <- input$map_shape_click

    y <- x$id

    return(y)

  })

# Drag event for the scatterplot; will grab tractids of selected points
sub <- reactive({

    eventdata <- event_data('plotly_selected', source = 'source')
    
    if (is.null(eventdata)) {
      
      return(NULL) # do nothing
      
    } else {
      
      precincts <- eventdata[['key']]
      
      if (length(precincts) == 0) {
        
        precincts <- 'abcdefg' # a hack but it's working - set to something that can't be selected
        
      }
      
      if (!(precincts %in% county_precincts()$dnc_id)) {
        
        return(NULL) # if there is not a match, do nothing as well
        
      } else {
        
        # Give back a sp data frame of the selected tracts
        sub <- county_precincts()[county_precincts()$dnc_id %in% precincts, ]

        return(sub)
        
      }
    
    }

  })

observe({

  req(sub()) # Do this if sub() is not null

  proxy <- leafletProxy('map')
  
  # Clear old selection on map, and add new selection
  proxy %>%
    clearGroup(group = 'sub') %>%
    addPolygons(data = sub(), fill = FALSE, color = '#00FFFF',
                opacity = 1, group = 'sub') %>%
    fitBounds(lng1 = bbox(sub())[1],
              lat1 = bbox(sub())[2],
              lng2 = bbox(sub())[3],
              lat2 = bbox(sub())[4])

})


observe({
  
  req(click_precinct()) # do this if click_tract() is not null
  
  # Add the clicked tract to the map in aqua, and remove when a new one is clicked
  map <- leafletProxy('map') %>%
      removeShape('hprecinct') %>%
      addPolygons(data = precincts_voter_data[precincts_voter_data$dnc_id == click_precinct(), ],
                  fill = FALSE,
                  color = '#FF00FF', opacity = 1, layerId = 'hprecinct')

  })



precinct_data <- reactive({
  
    # Fetch data for the clicked tract
    return(county_precincts()@data[county_precincts()@data$dnc_id == click_tract(), ])

  })


leafletOutput('map')  
```


Row
-----------------------------------------------------------------------

### Distance to Nearest Poll Place & Democrat Voters



Compare over time
============================================================================

Row
----------------------------------------------------------------------------